

# Harry Potter

books:

- Philosopher's Stone
- Chamber of Secrets
- Prisoner of Azkaban
- Goblet of Fire
- Order of the Phoenix
- Half-Blood Prince
- Deathly Hallows

```{r}
library(tidyverse)
library(tidytext)




# devtools::install_github("bradleyboehmke/harrypotter")
# books
# library(harrypotter)

# hp = harrypotter::philosophers_stone
# due to naming conflicts of the color palette of the
# same name I downloaded the data from the GitHub repo

load("./philosophers_stone.rda")

hp = philosophers_stone
```


Since Harry Potter books do not have chapters in the name like traditional books we could name
the chapters then append them to a data frame.

```{r}

chapters = c("THE BOY WHO LIVED",
             "THE VANISHING GLASS",
             "THE LETTERS FROM NO ONE",
             "THE KEEPER OF THE KEYS",
             "DRAGON ALLEY",
             "THE JOURNEY FROM PLAFORM NINE AND THREE-QUARTERS",
             "THE SORTING HAT",
             "THE POTIONS MASTER",
             "THE MIDNIGHT DUEL",
             "HALLOWEEN",
             "QUIDDITCH",
             "THE MIRROW OF ERUSED",
             "NICOLAS FLAMEL",
             "NORBERT THE NORWEGIAN RIDGEBACK",
             "THE FORBIDDEN FOREST",
             "THROUGH THE TRAPDOOR",
             "THE MAN WITH TWO FACES"
             )


hp_df = tibble( chapters = chapters, text = hp)

head(hp_df)

```


tokenize and clean up the text

```{r}

hp_df_tokens = hp_df %>% 
  unnest_tokens(input = text, output = word )


hp_clean = hp_df_tokens %>% 
  anti_join(stop_words, by='word')

head(hp_clean)
```


most common words by chapter, filter for words that occur more than 30 times

```{r}
hp_clean %>% 
  group_by(chapters, word) %>% 
  count(word, sort = T) %>% 
  ungroup() %>% 
  filter(n > 30)
```




```{r}
# -- color palette pkg
# install.packages("harrypotter")
library(harrypotter)

hp_clean %>% 
  group_by(word) %>% 
  count(word, sort = T) %>% 
  ungroup() %>% 
  top_n(20) %>% 
  ggplot(
    aes(x= n,
        y= reorder(word,n),
        fill= n
        )
  )+
  geom_col(show.legend = F)+
  ggdark::dark_mode()+
  scale_fill_hp(option = "Gryffindor")+
  labs(title = "Harry Potter: Philosophers Stone",
       subtitle = "Top 20 words",
       y="",
       x="word count"
       )+
  theme(
    plot.title = element_text(hjust = 0.5, 
                              size = 14),
    plot.subtitle = element_text(hjust = 0.5,
                                 size = 13),
    axis.text.y = element_text(size = 12, color = 'white')
  )+
  coord_cartesian(expand = F)
  
```



CLEANED BOOK !

```{r}
df = read_csv("philosophers_stone.csv")
head(df)
```











